\documentclass[a4paper,11pt]{article}
\usepackage[top=2cm, bottom=2cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{hyperref}

\title{Design \& Verification of a Dual-port Memory \\ as an APB subordinate (slave)}
\author{Nader Alnatsheh}
\date{\today}

\begin{document}
\maketitle

\newpage
\tableofcontents

\newpage
\section{Introduction}
The purpose of this project is to build a reusable verification environments to be used 
for my personal projects in the future. The verification enviroments are based on the 
SystemVerilog (SV) Object-Oriented Programming (OOP) methodology, 
and the Universal Verification Mehtodology (UVM). \\

Since the main focus is verification, the design used in the project is a simple 
dual-port memory 
\newpage

\section{Design Specs of the Dual-port Memory with an AMBA APB interfaces}

\subsection{Dual-port Memory Specs}

\subsubsection{Read Operation}
After the rising edge of the PENABLE signal the PRDATA provides the data after
2 clock cycles.

\subsubsection{Write Operation}
After the rising edge of the PENABLE signal the PWDATA copies the  the data after
2 clock cycles.

\begin{enumerate}
\item Addresses ranges from (0x0 - 0xf) are READ ONLY, and the manager (master) should not 
write to them, when the manager tries to write to a READ ONLY address, the subordinate
(slave) raises the PSLVERR signal after 1 clock cycle to indicates an error.

\item For all other Addresses the write operation takes 4 clock cycles. And the memory contents
updates on the 5th clock cycle.
\end{enumerate}

\subsection{AMBA APB Specs}
\subsubsection{Read Operation}
\subsubsection{Write Operation}

\newpage
\section{Verification Specs of the Dual-port Memory with an AMBA APB interface}

\newpage
\subsection{Test-plan}


\newpage
\subsection{OOP SV Environment}

\subsubsection{Transaction (Transaction.sv)}
The Transaction class contains:
\begin{enumerate}
\item The fields required to generate the randomized stimulus
\item Any constraints needed to constraint the randomized stimulus
\item Any functions that might be used in other classes. Since we will declare the Transaction as a handle in other classes
\end{enumerate}

\subsubsection{Generator}
The Generator class is responsible for:
\begin{enumerate}
\item Generating the stimulus by randomizing the Transaction class
\item Sending the randomized stimulus to the Driver class via a Mailbox. (Note: that the Mailbox handle will be coming from the Environment class, since the same Mailbox will be shared between the Generator and Driver classes)
\item An event is declared and will be used to indicate when the Generator class has finished generating the transactions
\end{enumerate}

\subsubsection{Driver}
The Driver class is responsible for:
\begin{enumerate}
\item Recieves the randomzied stimulus generated by the Generator class via the Mailbox
\item Drives the DUT by assigining the Transaction class values to the interface signals
\end{enumerate}
\subsubsection{Monitor}
\subsubsection{Scoreboard}
\subsubsection{Enviromnent}

\newpage
\subsection{UVM Environment}
\subsubsection{Sequence}
\subsubsection{Sequencer}
\subsubsection{Driver}
\subsubsection{Monitor}
\subsubsection{}
\subsubsection{}

\newpage
\section{References}

\end{document}